TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project Proposal}

### 2017-11-17 initial.tex
Update initial.tex

Our main research question is:
{\it How can a datacenter provide an available and reliable environment for
customers when multiple TCP congestion control algorithms are used in the
network?}

>>>>

Our main research question is:
{\it How can a datacenter provide an reliable and performant environment for
customers when multiple TCP congestion control algorithms are used in the
network?}
